
\section{Why should you use QB data?}

\begin{frame}{Summarization / Paraphrase}

\begin{itemize}
  \item Clues in quiz bowl questions are structured in \emph{increasing} order of importance
  \item Questions with same label are each structured summaries
    \begin{itemize}
      \item First clues are diverse
      \item Last clues are ``cannonical''
      \end{itemize}
  \item Thousands of different labels, some with hundreds of relevant questions
\end{itemize}

\end{frame}

\begin{frame}{Summarization / Paraphrase}
{\bf Choson Dynasty}
\begin{columns}
  \column{.45\linewidth}
  \begin{block}{First Clues}
    \begin{itemize}
    \item One tomb of a king \only<1>{from this region is named for the depiction of a eight-legged, ``Heavenly'' horse found there.} \invisible<1>{\dots}
    \item During this dynasty \only<2>{, a monk of the Son sect helped secure the release of over 3,000 prisoners of war.} \invisible<2>{\dots}
    \item Prince Sado of \only<3>{this dynasty was executed by being shut in a rice box, and its cloth tax was decreased by the Kyunyok Law.} \invisible<3>{\dots}
    \item During this dynasty, a Catholic \only<4>{scholar developed a philosophy of the rights of the people that is classified as part of the ``practical learning'' modernization movement known as Silhak.} \invisible<4>{\dots}
      \end{itemize}
  \end{block}
  \column{.45\linewidth}
  \begin{block}{Last Clues}
    \begin{itemize}
    \item Name this successor of the Goryeo \only<5>{Dynasty which ruled Korea for over five hundred years.} \invisible<5>{\dots}
    \item Name this dynasty that ruled Korea \only<6>{until annexed by Japan in 1910.} \invisible<6>{\dots}
    \item Name this dynasty which succeeded the Koryo, \only<7>{the longest lasting dynasty of Korea.} \invisible<7>{\dots}
    \item \only<8>{The successor of the Koryo dynasty, for 10 points,}\only<-7>{\dots} was what final imperial dynasty of Korea?
     \end{itemize}
  \end{block}

\end{columns}

\end{frame}

\begin{frame}{Coreference / Hypernym Extraction}

\begin{itemize}
  \item Good style in quiz bowl question requires all references to refer to the answer
  \item Forces diverse range in allowable references
\end{itemize}

\pause

\begin{block}{Hanseatic League}
\alert<3>{This entity} made a military pact known as the Tohopesate, and \alert<3>{it} was harassed by forces of Klaus Stortebeker, the leader of the Likedeelers, which were successors of pirates known as the Victual Brothers. After the humiliating Peace of Vordingborg, \alert<3>{this group} forced Valdemar IV of Denmark to sign the Treaty of Stralsund. The Peterhof in Novgorod and Steelyard in London are notable examples of Kontores established by \alert<3>{this polity}, although \alert<3>{its} power faded as the Swedish Empire lessened the importance of cities such as Visby and Lubeck. For 10 points, name \alert<3>{this Northern European trading league} which controlled the Baltic Sea.
\end{block}

\end{frame}
